\begin{thebibliography}{9}

\bibitem{} "GNU Octave", Gnu.org, 2016. [Online]. Available: http://www.gnu.org/software/octave/. [Accessed: 12- Mar- 2016].

\bibitem{} "Execute MATLAB/Octave Online", Tutorialspoint.com,2016. [Online]. Available: http://www.tutorialspoint.com/execute\_matlab\_online.php. [Accessed: 12- May- 2016].

\bibitem{} "Introduction to Linux", edx.org, 2016. [Online]. Available: https://www.edx.org/course/introduction-linux-linuxfoundationx-lfs101x-0. [Accessed: 31- Mar- 2016].

\bibitem{} "Try Octave in your browser!", Web Interface to Octave - project web site, 2010. [Online]. Available: http://knn.mimuw.edu.pl/weboctave-project/. [Accessed: 06- Apr- 2016].

\bibitem{} B.  Grewal, Numerical Methods in Engineering \& Science with Programs in C \& C++. New Delhi: Khanna, 2012.

\bibitem{} "Plotting Data with gnuplot", 2016. [Online]. Available: https://www.cs.hmc.edu/~vrable/gnuplot/using-gnuplot.html. [Accessed: 24- Feb- 2016].

\bibitem{} "Numerical Analysis", WIKIPEDIA, 2016. [Online]. Available: https://en.wikipedia.org/wiki/Numerical\_analysis. [Accessed: 06- Apr- 2016].

\bibitem{} "BISECTION METHOD", 2016. [Online]. Available: https://mat.iitm.ac.in/home/sryedida/public\_html/caimna/transcendental/bracketing\%20methods/bisection/bisection.html. [Accessed: 16- May- 2016].

\bibitem{} "Gauss elimination and Gauss Jordan methods using MATLAB code", GitHub Gist, 2016. [Online]. Available: https://gist.github.com/esromneb/1d57b1d16d54cde37332. [Accessed: 22- May- 2016].

\bibitem{} "GreatDevelopers/Weboctave", GitHub, 2016. [Online]. Available: https://github.com/GreatDevelopers/Weboctave. [Accessed: 28- Mar- 2016].

\bibitem{} "pritikamalhotra/NMCE", GitHub, 2016. [Online]. Available: https://github.com/pritikamalhotra/NMCE. [Accessed: 22- Mar- 2016].

\bibitem{} P.  Malhotra, "WebOctave", Knowledge is one that gives wisdom", 2016. 
\end{thebibliography}
