\section{Technical and Managerial Lesson Learnt}
I learned a lot by doing this project . During this period I got to learn a vast 
number of technologies. These are lsited below :
\begin{itemize}
\item {\bf{Operating system}}: Ubuntu
\item {\bf{Languages used}}: Python, Html, CSS, JavaScript
\item {\bf{Framework}}: Django 
\item {\bf{Database}}: MySql
\item {\bf{Typesetting}}: LaTex
\item {\bf{Documenter}}: Doxygen

\end{itemize}
So during this project I learned all the above things. Above all I got to know 
how Softwares are developed from the scratch. Planning, designing, developing code, 
working in a team, testing etc. These are all very precious things I got to learn 
during this period. If I talk about the project, Automation project reduce lot of 
manual work. It has automated most of the office work of Freight Carriers.  

\section{Current status}
OFC Automation software is currently running in Open Freight Carriers.It has 
automated most of the office work of Freight Carriers.
Software has following applications in it:
\begin{itemize}
\item Login and registration
\item Add new Consignment.
\item Search previous Consignments.
\item Generate consignmnet note.
\item Checking dispatch Status.
\end{itemize}
 
\section{Future Scope}
Automation software reduces the manual work and save the money. It also reduces 
the man power and reduces the burden of handling lots of data. It keeps the backup 
of the record stored. As the project is complete but still there are many more 
things or areas which can be added to the project to make that more reliable. 
These remaining areas may be:
\begin{enumerate}
\item Recieve the payment online through e-billing.
\item E-mail or mobile notification on successfull delievry.
\item Consignment Note Fax: There may be an option through which the consignment 
will be automatically faxed to the Clients.
\end{enumerate}


